Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-01 manuscript/manuscript.tex
typos

While it challenging to apply temporal methods to natural populations
there is a lot of promise for these approaches \cite{Dmitri_others}. 
Efforts to estimate the quantify the impact of linked selection in
humans and {\it Drosophila melanogaster} have suggested that XXX to
XXX of allele frequency change over long time periods is driven by
selection \citep{}. Thus there is reason to be hopeful that we could
detect this from temporal data, which would help to resolve the
time-scales that linked selection act over. In our reanalysis of the \textcite{Barghi2019-qy} study, we find evidence
of complex linked selection dynamics, with selection pressures
flipping over time due to either environmental change, the breakup of
epistatic combinations or advantagous haplotypes. Such patterns would
 be completely obscured in samples only from contempory populations,
 thus we can hope tyo have a much richer picture of linked selection
 as temporal sequencing becomes more common.

>>>>

While it challenging to apply temporal methods to natural populations
there is a lot of promise for these approaches \cite{Dmitri_others}. 
Efforts to estimate the quantify the impact of linked selection in
have suggested that XXX to
XXX of allele frequency change over long time periods is driven by
selection \parencite{Mcvicker,Comeron,Elyashiv2016-vt,Russ,Coop}. Thus there is reason to be hopeful that we could
detect this from temporal data, which would help to resolve the
time-scales that linked selection act over. In our reanalysis of the \textcite{Barghi2019-qy} study, we find evidence
of complex linked selection dynamics, with selection pressures
flipping over time due to either environmental change, the breakup of
epistatic combinations or advantagous haplotypes. Such patterns would
 be completely obscured in samples only from contempory populations,
 thus we can hope to have a much richer picture of linked selection
 as temporal sequencing becomes more common.
